---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# dMeasureAppointments

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of dMeasureAppointments is to provide appointment-related functions and views for dMeasure/GPstat!

## Installation

You can install the released version of dMeasureAppointments with:

``` r
remotes::install_github("DavidPatShuiFong/dMeasureAppointments")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(dMeasureAppointments)
## basic example code
```


## Code of Conduct
  
Please note that the dMeasureAppointments project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
